BurgerTown Presents: Open Adcess

### 2017-04-10 openadcess.tex
Took a stab at the intro
Related work
Conclusion and future work fill ins

\title{\todo{Something} presents OpenAdcess}
\maketitle

\begin{abstract}
  In this paper we examine an alternate funding model for open access papers.
  Through modest modifications to the ACM Digital Library and the addition of
  paper sponsorships we can make the entire corpus of ACM works free to the
  public.
  We also peer into a chilling future that only we can prevent.
  Will we stop the ACM from encroaching on our everyday freedoms?
  Continue existing and participating in reality to find out!
\end{abstract}

\section{Introduction}

\section{Related Work}

@@

>>>>

\title{BurgerTown Presents: Open Adcess}
\maketitle

\begin{abstract}
  In this paper we examine an alternate funding model for open access papers.
  Through modest modifications to the ACM Digital Library and the addition of
  paper sponsorships, we can make the entire corpus of ACM works free to the
  public. What does the future have in store for the open-adcess movement?
  Continue existing and participating in reality to find out!
\end{abstract}

\input{introduction}

\input{related-work}

@@

\input{conclusion}

\bibliography{references}{}
\bibliographystyle{plain}
